%!TEX root = ../Thesis.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \textsc{Abstract}
\end{center}
\noindent

In this thesis, we presented a novel edge bundling technique based on a Physarium approximation of a Steiner tree. Here we use the Steiner tree as a routing structure for graph paths. The resulting drawings consist of densely bundled graphs that reduce node-edge overlaps and make it easier to get an overview of the graph data.

For the Physarium calculation, we utilize the network Poisson equation to simulate a liquid flow inside the graph network, which enables us to cut nodes and edges, if the conductivity in an edge gets too low. Cutting edges shrinks the network until just a Steiner tree is left. To optimize the process, we multithreaded the calculation and found optimal iteration bounds that still deliver a satisfactory approximation result.
To visualize the initial network paths, we route them via the Steiner tree and visualize them by utilizing B\'{e}zier curves.

The outcomes enhance readability and make spotting areas of interest more straightforward. We further evaluate our algorithm by calculating the quality metrics: ink reduction, distortion, and ambiguity. We compare the results to two edge bundling approaches to classify our technique and comprehend its usefulness. We additionally discuss the constraints of our method and propose further improvements to circumvent these limitations.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cleardoublepage
